---
title: "Alevin, Seurat single cell analysis for AALE Manuscript"
author: "Roman Reggiardo"
date: "4/7/2020"
output: 
  html_notebook:
    highlight: pygments
editor_options: 
  chunk_output_type: console
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/home/rreggiar/notebooks')
```
## Figure Code for *insert link here* {.tabset .tabset-fade .tabset-pills}
### On board
```{r echo=FALSE}
# Run this cell to load in all packages used in the notebook
suppressPackageStartupMessages({
  library(tidyverse)
  #library(ggsci)
  library(ggpubr)
  library(ggsignif)
  library(ggthemes)
  library(ggrepel)
  library(ggforce)
  library(SingleCellExperiment)
  library(tximport)
  library(extrafont)
  library(Seurat)
  library(msigdbr)
  #library(GGally)
  library(viridis)
  #library(ggtern)
  library(patchwork)
  library(Hmisc)
})


suppressMessages(loadfonts())
```
### Figure themes for publication
```{r echo=FALSE}
## style sheets, one as a document wide arg, one as a function 
## the function works with some of the suerat-wrapped plotting functions
theme_set(theme_foundation(base_size = 7, base_family = 'Helvetica') + 
            theme(plot.title = element_blank(),
                panel.background = element_rect(colour = NA),
                plot.background = element_rect(colour = NA),
                panel.border = element_rect(colour = NA),
                axis.title = element_text(face = "bold",size = rel(1)),
                axis.title.y = element_text(angle=90,vjust =2),
                axis.title.x = element_text(vjust = -0.2),
                axis.text = element_text(), 
                axis.line = element_blank(),
                strip.text = element_text(),
                strip.background = element_blank(),
                legend.key.size= unit(0.2, "cm"),
                legend.spacing = unit(0, "cm"),
                legend.key = element_rect(colour = NA),
                legend.title = element_text(face="italic"),
                legend.text = element_text(face = 'bold'),
                plot.margin=margin(10,5,5,5,unit = "mm"),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
          ))

set_aale_theme  <- function(){theme_set(theme_foundation(base_size = 7, base_family = 'Helvetica') + 
            theme(plot.title = element_blank(),
                panel.background = element_rect(colour = NA),
                plot.background = element_rect(colour = NA),
                panel.border = element_rect(colour = NA),
                axis.title = element_text(face = "bold",size = rel(1)),
                axis.title.y = element_text(angle=90,vjust =2),
                axis.title.x = element_text(vjust = -0.2),
                axis.text = element_text(), 
                axis.line = element_blank(),
                strip.text = element_text(),
                strip.background = element_blank(),
                legend.key.size= unit(0.2, "cm"),
                legend.spacing = unit(0, "cm"),
                legend.key = element_rect(colour = NA),
                legend.title = element_text(face="italic"),
                legend.text = element_text(face = 'bold'),
                plot.margin=margin(10,5,5,5,unit = "mm"),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank()
            ))}
```
### Gene sets of interest
```{r echo=FALSE}
## manually curated from publications **SHOULD ADD LINKS**
## or using the MSIGDBR library and doing some string matching
kras.isg.signature <- c("DDX58", "IFIH1", "IFNL1", "IRF9", "IFI27", "OAS2", "IFIT3", "IFIT1", "OASL", "ISG15", "OAS3", "RSAD2", "MX1", "OAS1", "IFI44", "CH25H", "IFIT2", "ISG20", "RNASEL", "IFI6", "HERC5", "HERC6", "GBP3", "GBP1", "IRF1", "ISG15")

liu.isg.signature <- c('ADAR', 'DDX60', 'HERC6', 'IRF7', 'OASL', 'PSM2', 'STAT2', 'TRIM25', 'BST2', 'DHX58', 'IFI35',
                       'ISG15', 'OGFR', 'RSAD2', 'TDRD7', 'UBE2L6', 'CASP1', 'EIF2AK2', 'IFIH1', 'ISG20', 'PARP12',
                       'RTP4', 'TRAFD1', 'USP18', 'CMPK2', 'EPSTI1', 'IFIT2', 'MX1', 'PARP14', 'SAMD9L', 'TRIM14',
                       'CXCL10', 'GBP4', 'IFIT3', 'NMI', 'PNPT1', 'SP110', 'TRIM21')

gs.names = c("KRAS ISG SIGNATURE" , 
             "LIU ISG SIGNATURE" ,
             'HALLMARK IFNA RESPONSE',
             'HALLMARK IFNG RESPONSE',
             'HALLMARK KRAS UP')

rig.i.mda5.induction <- 
  msigdbr(species = 'Homo sapiens') %>% 
  subset(grepl('REACTOME_DDX58', gs_name)) %>% 
  mutate(gs_name = 'RIG_I_MDA5_INDUCTION') %>% 
  select(gene_symbol) %>% 
  unlist() %>% 
  unname()

rig.i.mda5.neg.regulation <- 
  msigdbr(species = 'Homo sapiens') %>% 
  subset(grepl('OF_DDX58', gs_name)) %>% 
  mutate(gs_name = 'RIG_I_MDA5_NEG_REGULATION') %>% 
  select(gene_symbol) %>% 
  unlist() %>% 
  unname()

msig.df.h.ifng <- 
  msigdbr(species = 'Homo sapiens', category = 'H') %>% 
  subset(grepl('_GAMMA_RESPONSE', gs_name)) %>% 
  mutate(gs_name = 'HALLMARK_IFNG_RESPONSE') %>% 
  select(gene_symbol) %>% 
  unlist() %>% 
  unname()

msig.df.h.ifna <- 
  msigdbr(species = 'Homo sapiens', category = 'H') %>% 
  subset(grepl('_ALPHA_RESPONSE', gs_name)) %>% 
  mutate(gs_name = 'HALLMARK_IFNA_RESPONSE') %>% 
  select(gene_symbol) %>% 
  unlist() %>% 
  unname()

kras.signal.up <- 
  msigdbr(species = 'Homo sapiens') %>% 
  filter(gs_name == 'HALLMARK_KRAS_SIGNALING_UP')  %>% 
  select(gene_symbol) %>% 
  unlist() %>% 
  unname()

```
### import and QA
```{r}
# load in alevin quant matrix as a seurat object, assess standard measurements
set.seed(431)

files <- 
  file.path('data/single.cell.rna.seq/output/gencode.te.locus.v.1.index.alevin.out/alevin/quants_mat.gz')
file.exists(files)

txi <- tximport(files, type="alevin")

kras.aale.sc <- CreateSeuratObject(counts = txi$counts, min.cells = 3, 
                                   min.features = 200, project = "KRAS.AALE")

kras.aale.sc[["percent.mt"]] <- PercentageFeatureSet(kras.aale.sc, pattern = "^MT-")
kras.aale.sc[["percent.rp"]] <- PercentageFeatureSet(kras.aale.sc, pattern = '^RP')

VlnPlot(kras.aale.sc, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"))
plot1 <- FeatureScatter(kras.aale.sc, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(kras.aale.sc, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
plot3 <- FeatureScatter(kras.aale.sc, feature1 = "nCount_RNA", feature2 = "percent.rp")
# scatter plot of MT, RNA, Ribo
CombinePlots(plots = list(plot1, plot2, plot3))
```
### filter and PCA
```{r}
## Filter according to seurat guidelines
## I've reworked this extensively and, due to the relatively small number of truly variable genes and cells, I've filtered heavily
## these settings seem to provide the most robust characterization of the immune phenotype we're seeing
set.seed(431)

kras.aale.sc <- subset(kras.aale.sc, 
                       subset = nFeature_RNA >= 2000  & 
                         percent.mt < 5 & 
                         nFeature_RNA <= 7000)

kras.aale.sc <- NormalizeData(kras.aale.sc, 
                              normalization.method = "LogNormalize", scale.factor = 10000)

kras.aale.sc <- FindVariableFeatures(kras.aale.sc, selection.method = "vst", nfeatures = 500)

# vector of all remaining genes in the seurat object
all.genes <- rownames(kras.aale.sc)

kras.aale.sc <- ScaleData(kras.aale.sc, features = all.genes)
kras.aale.sc <- RunPCA(kras.aale.sc, features = VariableFeatures(object = kras.aale.sc))

# jackstraw is just for EDA, arguments here won't affect the clustering, but results should be used to aid
# in determining appropriate UMAP args
kras.aale.sc <- JackStraw(kras.aale.sc, num.replicate = 100)
kras.aale.sc <- ScoreJackStraw(kras.aale.sc, dims = 1:20)

JackStrawPlot(kras.aale.sc, dims = 1:20)

ElbowPlot(kras.aale.sc)


```
### UMAP and cluster
```{r}
## run clustering via suerat with manually determined args
set.seed(431)
# knn, umap
kras.aale.sc <- FindNeighbors(kras.aale.sc, dims = 1:10)
kras.aale.sc <- FindClusters(kras.aale.sc, resolution = 0.6)
kras.aale.sc <- RunUMAP(kras.aale.sc, dims = 1:10)
# assess QC features on a cluster-to-cluster basis to detect bias
VlnPlot(kras.aale.sc, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"))

# note that you can set `label = TRUE` or use the LabelClusters function to help label
# individual clusters
DimPlot(kras.aale.sc, 
        reduction = "umap", 
        pt.size = 0.42,  
        cols = c(viridis(12, option = 'plasma')[1],
                 viridis(12, option = 'inferno')[2],
                 viridis(12, option = 'D')[5],
                 viridis(12, option = 'plasma')[7],
                 viridis(12, option = 'inferno')[9],
                 viridis(12, option = 'D')[11],
                 viridis(12, option = 'magma')[6],
                 viridis(12, option = 'magma')[3])) + 
  set_aale_theme()

ggsave('figures/fig.1/umap.sc.3x3.pdf', height = 3, width = 3, units = 'in')
```
### marker genes
```{r}
## use seurat functionality to isolate 'marker genes' from each cluster
kras.aale.sc.markers <- 
  FindAllMarkers(kras.aale.sc, 
                 only.pos = F, 
                 min.pct = 0.25, 
                 logfc.threshold = 0.25) %>% 
  filter(p_val_adj < 0.01)
# filter down to the top 5 most significant markers per cluster
kras.aale.sc.markers.heatmap <- 
  kras.aale.sc.markers %>% 
  group_by(cluster) %>% 
  top_n(n = 5, wt = -p_val) 
# filter down to the top 10 most sig in cluster 4
kras.aale.sc.markers %>% 
  group_by(cluster) %>% 
  top_n(n = 10, wt = avg_logFC) %>% 
  filter(cluster %in% c(4)) %>%
  ungroup() %>% 
  select(gene) %>%
  unname() %>% 
  unlist() -> isg.markers
```
### Plotting normalized counts -- UNDER CONSTRUCTION
```{r}
###
# UNDER CONSTRUCTION
# needs to be updated and functionalized
###

# extract scaled, normalized counts
kras.aale.sc.norm.counts <- as.data.frame(as.matrix(kras.aale.sc[["RNA"]]@scale.data))
# extract barcodes
kras.barcode.counts <- 
  as.data.frame(as.matrix(kras.aale.sc@active.ident)) %>% 
  rownames_to_column('barcode')
# rename column to reflect data
names(kras.barcode.counts)[2] <- 'cluster'
# tidy 
kras.aale.sc.norm.counts <- 
  kras.aale.sc.norm.counts %>% 
  rownames_to_column('gene') %>% 
  gather(barcode, norm.counts, -gene) 
# pair barcodes and counts
kras.aale.sc.norm.counts <- 
  merge(kras.aale.sc.norm.counts, kras.barcode.counts, by = 'barcode')
# make TE class gene sets
alu.gene.set <- subset(kras.aale.sc.norm.counts, grepl('^Alu', gene))$gene
fram.gene.set <- subset(kras.aale.sc.norm.counts, grepl('FRAM', gene))$gene
mer.gene.set <- subset(kras.aale.sc.norm.counts, grepl('^MER', gene))$gene
herv.gene.set <- subset(kras.aale.sc.norm.counts, grepl('^HERV', gene))$gene
ltr.gene.set <- subset(kras.aale.sc.norm.counts, grepl('^LTR', gene))$gene
line.gene.set <- subset(kras.aale.sc.norm.counts, grepl('^L1', gene))$gene
cd47.gene.set <- subset(kras.aale.sc.norm.counts, gene == 'CD47')$gene
# make znf gene set
znfs.gene.set <- c('ZFP92', 'ZNF135', 'ZNF334', 'ZNF34', 'ZNF347', 'ZNF345A', 'ZNF345C',
                     'ZNF382', 'ZNF415', 'ZNF433', 'ZNF441', 'ZNF442', 'ZNF471', 'ZNF506',
                     'ZNF528', 'ZNF558', 'ZNF563', 'ZNF568', 'ZNF582', 'ZNF586', 'ZNF605',
                     'ZNF655', 'ZNF662', 'ZNF667', 'ZNF682', 'ZNF736', 'ZNF788', 'ZNF793',
                     'ZNF814', 'ZNF83', 'ZNF880', 'ZNF90', 'ZNF10', 'ZNF133', 'ZNF665', 'ZNF699',
                     'ZNF792')
gene.set.list <- c(alu.gene.set,
                   mer.gene.set,
                   herv.gene.set,
                   ltr.gene.set,
                   line.gene.set,
                   fram.gene.set,
                   znfs.gene.set,
                   cd47.gene.set,
                   liu.isg.signature,
                   kras.isg.signature,
                   rig.i.mda5.induction,
                   rig.i.mda5.neg.regulation,
                   msig.df.h.ifna,
                   msig.df.h.ifng,
                   kras.signal.up)


# spread data into gene columns
norm.counts.plot <- 
  kras.aale.sc.norm.counts %>% 
  group_by(barcode) %>% 
  subset(gene %in% gene.set.list) %>%
  spread(gene, norm.counts)
##USED
isg.heatmap.norm.counts.plot <- 
  kras.aale.sc.norm.counts %>% 
  group_by(barcode) %>% 
  subset(gene %in% c(isg.markers, 'DDX58', 'IFIH1')) %>%
  spread(gene, norm.counts)

## USED
isg.anno.df <- data.frame('cluster' = c(4,2,1,0,3)) %>%
  mutate(cluster = as.factor(cluster))
rownames(isg.anno.df) <- isg.anno.df$cluster

## USED
isg.anno.colors <- list(cluster = c(`0` = viridis(12, option = 'plasma')[1],
                 `1` = viridis(12, option = 'inferno')[2],
                 `2` = viridis(12, option = 'D')[5],
                 `3` = viridis(12, option = 'plasma')[7],
                 `4` = viridis(12, option = 'inferno')[9]))
### USED
isg.marker.heatm <- 
  isg.heatmap.norm.counts.plot %>%
  gather(gene, count, -barcode, -cluster) %>% 
  mutate(gene = ifelse(gene == 'DDX58', 'RIG-I', gene),
         gene = ifelse(gene == 'IFIH1', 'MDA5', gene)) %>% 
  group_by(cluster, gene) %>% 
  summarise(mean.count = mean(count)) %>% 
  ungroup() %>% 
  mutate(mean.count = log2(mean.count + 1)) %>% 
  filter(!is.na(mean.count)) %>% 
  spread(cluster, mean.count) %>% 
  column_to_rownames('gene') %>% 
  pheatmap::pheatmap(color = viridis(512), 
                     border_color = NA, 
                     treeheight_col = 15, 
                     treeheight_row = 15,
                     fontsize = 7,
                     show_colnames = F,
                     width = 3, height = 3, angle_col = 0,
                     annotation = isg.anno.df,
                     annotation_colors = isg.anno.colors) 
  
ggsave(plot = isg.marker.heatm, 
       'figures/fig.1/isg.cluster.markers.heatmap.3x3.pdf', 
       height = 3, width = 3, units = 'in')



norm.counts.present.alu.gene.set <- 
  colnames(norm.counts.plot) %>% 
  subset(. %in% c(alu.gene.set)) 

norm.counts.present.fram.gene.set <- 
  colnames(norm.counts.plot) %>% 
  subset(. %in% fram.gene.set)

norm.counts.present.mer.gene.set <- 
  colnames(norm.counts.plot) %>% 
  subset(. %in% c(mer.gene.set)) 

norm.counts.present.herv.gene.set <- 
  colnames(norm.counts.plot) %>% 
  subset(. %in% c(herv.gene.set)) 

norm.counts.present.ltr.gene.set <- 
  colnames(norm.counts.plot) %>% 
  subset(. %in% c(ltr.gene.set)) 

norm.counts.present.line.gene.set <- 
  colnames(norm.counts.plot) %>% 
  subset(. %in% c(line.gene.set)) 

norm.counts.present.znfs.gene.set <- 
  colnames(norm.counts.plot) %>% 
  subset(. %in% c(znfs.gene.set)) 

norm.counts.present.kras.isg.gene.set <- 
  colnames(norm.counts.plot) %>% 
  subset(. %in% c(kras.isg.signature)) 

norm.counts.present.rig.i.mda5.gene.set <- 
  colnames(norm.counts.plot) %>% 
  subset(. %in% c(rig.i.mda5.induction)) 

norm.counts.plot$rig_i_ind <- 
  rowMeans(norm.counts.plot[, norm.counts.present.kras.isg.gene.set])

norm.counts.plot$kras_isg <- 
  rowMeans(norm.counts.plot[, norm.counts.present.rig.i.mda5.gene.set])



norm.counts.plot$TE.AVG <- 
  rowMeans(norm.counts.plot[, c(norm.counts.present.alu.gene.set,
                            norm.counts.present.mer.gene.set,
                            norm.counts.present.herv.gene.set, 
                            norm.counts.present.ltr.gene.set, 
                            norm.counts.present.line.gene.set,
                            norm.counts.present.fram.gene.set)])
norm.counts.plot$ALU <- 
  rowMeans(norm.counts.plot[, norm.counts.present.alu.gene.set])
norm.counts.plot$MER <- 
  rowMeans(norm.counts.plot[, norm.counts.present.mer.gene.set])
norm.counts.plot$HERV <- 
  rowMeans(norm.counts.plot[, norm.counts.present.herv.gene.set])
norm.counts.plot$LTR <- 
  rowMeans(norm.counts.plot[, norm.counts.present.ltr.gene.set])
norm.counts.plot$LINE <- 
  rowMeans(norm.counts.plot[, norm.counts.present.line.gene.set])
norm.counts.plot$ZNF <- 
  rowMeans(norm.counts.plot[, norm.counts.present.znfs.gene.set])
norm.counts.plot$CD47 <- 
  rowMeans(norm.counts.plot[, norm.counts.present.cd47.gene.set])

norm.counts.plot.final <- 
  norm.counts.plot %>% 
  select(barcode, cluster, ALU, MER, HERV, LTR, LINE, TE.AVG, ISG.GS, ISG.RS, ZNF,
         CD47, DER.IFN.ALPHA.UP, DER.IFN.BETA.UP, DER.IFN.GAMMA.UP, 
         RIG.I.MDA.5.INDUCTION)

norm.counts.p.mat <- 
  cor_pmat(subset(norm.counts.plot.final, cluster == 2)[,-c(1,2)])

gene.set.cor.df <- 
  cor(subset(norm.counts.plot.final)[,-c(1,2)])

ggcorrplot::ggcorrplot(gene.set.cor.df, lab = T)


cluster.id.color.lookup <- tibble(cluster = c(0,1,2,3,4,5),
                                  color = c('#440154FF',
                 '#404788FF',
                 '#2D708EFF',
                 '#20A387FF',
                 '#73D055FF',
                 '#FDE725FF'))
## USED
ggplot(norm.counts.plot %>% filter(cluster %in% c(2,4)), 
       aes(rig_i_ind, kras_isg, color = cluster)) + 
  geom_point(size = 0.42) +
  scale_color_manual(values = c(viridis(12, option = 'D')[5], viridis(12, option = 'inferno')[9])) + 
  ylab('KRAS ISG') +
  xlab('RIG I / MDA5 INDUCTION') + 
  facet_row(~cluster, scales = 'free') + 
  geom_smooth(method = 'lm', se = F, size = 0.42) + 
  ggpubr::stat_cor(show.legend = F, inherit.aes = T, size = rel(2), 
                   label.x.npc = 'left', label.y.npc = 1) +
  set_aale_theme() + 
  theme(strip.text = element_blank(),
  plot.margin =  margin(-.5,1,.35,1,unit = "mm"))

  

ggsave('figures/fig.1/rig.i.v.kras.isg.scatter.label.1.5x3.pdf', height = 1.5, width = 3, units = 'in')

```
#### funciton(correlation) -- UNDER CONSTRUCTION
```{r}
make.gene.set.cor.plot <- function(cluster.choice, x.val , y.val){

  gene.set.cor.df <- 
  cor(subset(norm.counts.plot.final, cluster == cluster.choice)[,-c(1,2)])
  gene.set.cor.small <- 
  gene.set.cor.df[! colnames(gene.set.cor.df) %in% c('ALU', 'FRAM', 
                                                   'MER', 'HERV', 
                                                   'LTR', 'LINE', 'TE.AVG', 'ZNF', 'CD47'),
                  ! rownames(gene.set.cor.df) %in% c('ISG.GS', 'ISG.RS', 
                                                   'DER.IFN.ALPHA.UP', 'DER.IFN.BETA.UP', 
                                                   'DER.IFN.GAMMA.UP', 'RIG.I.MDA.5.INDUCTION')]

  tidy.gene.set.cor.small <- 
    gene.set.cor.small %>% 
    as.data.frame() %>% 
    rownames_to_column('compare') %>% 
    gather(te.set, pearson, -compare) %>% 
    ggplot(aes(compare, te.set, 
               fill = pearson,
               label = round(pearson, 2))) + 
    geom_tile() + 
    geom_text(size = 2, color = 'white', alpha = 1) +
    scale_alpha_continuous(guide = F, breaks = c(-0.25, 0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.8)) + 
    scale_fill_viridis_c(limits = c(-0.25, 0.75), direction = -1) + 
    xlab('') + ylab('') + 
    theme(axis.text.x = element_text(angle = 40, hjust = 1)) + 
    scale_y_discrete(limits = c('MER', 'LINE', 'LTR', 'HERV', 'ALU', 'TE.AVG', 'ZNF', 'CD47')) + 
    scale_x_discrete(limits = c('ISG.GS',
                                'ISG.RS',
                                'DER.IFN.ALPHA.UP',
                                'DER.IFN.BETA.UP',
                                'DER.IFN.GAMMA.UP',
                                'RIG.I.MDA.5.INDUCTION'))
  
  cluster.id.color <- cluster.id.color.lookup$color[cluster.id.color.lookup$cluster == cluster.choice]
  
  scatter.plot <- 
    ggplot(subset(norm.counts.plot.final, ALU > -3 & cluster == cluster.choice), 
       aes_string(x = x.val, 
                  y = y.val)) + 
  geom_point(alpha = 0.4,
       color = cluster.id.color) + 
  geom_rug( color = cluster.id.color) 
  
  list(cluster.id.color.lookup$color[cluster.id.color.lookup$cluster == cluster.choice], tidy.gene.set.cor.small, scatter.plot)
}

make.gene.set.cor.plot(2, x.val = 'CD47', y.val = 'RIG.I.MDA.5.INDUCTION')
```
### Plotting normalized abundance of 'metagenes'
```{r}
## using seurat wrappers for GGPLOT functions to visualize the means of gene sets on a per cell/per cluster basis
# make a copy so we don't overwrite everything above accidentallu
gene.set.kras.aale.sc <- kras.aale.sc  
# add the gene set as an attribute of the single cell object (requires the SCexperiment library)
add.gene.set.to.sc <- function(gene.set, name){
  gene.set <- 
    rownames(gene.set.kras.aale.sc[['RNA']]@data)[rownames(gene.set.kras.aale.sc[['RNA']]@data) %in% gene.set]
  
  # Get mean expression of genes of interest per cell
  mean.exp <- 
    colMeans(x = gene.set.kras.aale.sc[['RNA']]@data[rownames(gene.set.kras.aale.sc[['RNA']]@scale.data) %in% gene.set,], na.rm = TRUE)
  
  # Add mean expression values in 'object@meta.data$gene.set.score'
  name <- deparse(substitute(name))
  gene.set.kras.aale.sc@meta.data[, `name`] <- mean.exp 
  return(gene.set.kras.aale.sc)
}
# need to pass the name like this in order to use it as a string...unless I overcomplicated things
gene.set.kras.aale.sc <- add.gene.set.to.sc(liu.isg.signature, `liu.isg.signature`)
gene.set.kras.aale.sc <- add.gene.set.to.sc(kras.isg.signature, `kras.isg.signature`)
gene.set.kras.aale.sc <- add.gene.set.to.sc(msig.df.h.ifna, `msig.df.h.ifna`)
gene.set.kras.aale.sc <- add.gene.set.to.sc(msig.df.h.ifng, `msig.df.h.ifng`)
gene.set.kras.aale.sc <- add.gene.set.to.sc(kras.signal.up, `kras.signal.up`)
gene.set.kras.aale.sc <- add.gene.set.to.sc(rig.i.mda5.induction, `rig.i.mda5.induction`)
gene.set.kras.aale.sc <- add.gene.set.to.sc(rig.i.mda5.neg.regulation, `rig.i.mda5.neg.regulation`)
# have a special style sheet to get the multi-panel look right
vln_theme <- function() {theme_set(theme_foundation(base_size = 7, base_family = 'Helvetica') + 
            theme(plot.title = element_blank(),
                panel.background = element_rect(colour = NA),
                plot.background = element_rect(colour = NA),
                panel.border = element_rect(colour = NA),
                axis.title = element_text(face = "bold",size = rel(1)),
                axis.title.y = element_text(angle=90,vjust =2),
                axis.title.x = element_blank(),
                axis.text = element_text(), 
                axis.line = element_blank(),
                strip.text = element_text(),
                strip.background = element_blank(),
                legend.key.size= unit(0.2, "cm"),
                legend.spacing = unit(0, "cm"),
                legend.title = element_text(face="italic"),
                legend.text = element_text(face = 'bold'),
                plot.margin=margin(10,5,5,5,unit = "mm"),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                legend.position = 'NA'
          ))
}
# making the plot objects
make.gene.set.vln <- function(name){
  
  name <- deparse(substitute(name))

  return(VlnPlot(gene.set.kras.aale.sc, 
        features = `name`, 
        nrow = 1, pt.size = 0, size = 0.5, 
        cols = c(viridis(12, option = 'plasma')[1],
                 viridis(12, option = 'inferno')[2],
                 viridis(12, option = 'D')[5],
                 viridis(12, option = 'plasma')[7],
                 viridis(12, option = 'inferno')[9],
                 viridis(12, option = 'D')[11])) + 
  xlab('') + 
    vln_theme() + 
    theme(legend.position = 'null'))

}



liu.isg.vln <- make.gene.set.vln(`liu.isg.signature`)
kras.isg.vln <- make.gene.set.vln(`kras.isg.signature`)
msig.df.h.ifna.vln <- make.gene.set.vln(`msig.df.h.ifna`)
msig.df.h.ifng.vln <- make.gene.set.vln(`msig.df.h.ifng`)
kras.signal.up.vln <- make.gene.set.vln(`kras.signal.up`)
rig.i.mda5.induction.vln <- make.gene.set.vln(`rig.i.mda5.induction`)
rig.i.mda5.neg.regulation.vln <- make.gene.set.vln(`rig.i.mda5.neg.regulation`)
# pasting them into a single panel
patchwork::wrap_plots(list(kras.signal.up.vln,liu.isg.vln, msig.df.h.ifna.vln,kras.isg.vln))
ggsave('figures/fig.1/stacked.vln.3x4.pdf', height = 3, width = 4, units = 'in')

make.gene.vln <- function(name){
  
  name <- deparse(substitute(name))

  return(VlnPlot(gene.set.kras.aale.sc, 
        features = c(`name`), 
        nrow = 1, pt.size = 0.42, size = 0.5, 
        cols = c(viridis(12, option = 'plasma')[1],
                 viridis(12, option = 'inferno')[2],
                 viridis(12, option = 'D')[5],
                 viridis(12, option = 'plasma')[7],
                 viridis(12, option = 'inferno')[9],
                 viridis(12, option = 'D')[11])) + 
  xlab('') + 
  vln_theme() + 
  scale_y_continuous(limits = c(-0.01,1.3)) + 
  theme(legend.position = 'null',
        plot.margin =  margin(-10,0,-5,0,unit = "mm")))

}

## do the same thing but for individual genes
ddx58.vln <- make.gene.vln(`DDX58`) 

ifih1.vln <- make.gene.vln(`IFIH1`) + ylab('') 

ddx58.vln + ifih1.vln
patchwork::wrap_plots(list(ddx58.vln, ifih1.vln), ncol = 2)
ggsave('figures/fig.1/dsRNA.sensor.vln.1x3.pdf', height = 1, width = 3, units = 'in')
```
### Export *Seurat* object to loom for import into scanpy:
```{r}
library(scater)
library(loomR)

kras.aale.sc@graphs <- list()

kras.aale.sc.loom <- as.loom(kras.aale.sc,
                             filename = '../data/kras.aale.sc.te.loom',
                             verbose = F)

kras.aale.sc.loom
kras.aale.sc.loom$close_all()
```
